Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-08-29 analysis/paper/paper.qmd
update dockerfile

Compared to the  Phase 2 and 3, we found that there are only minor differences between the two phases. The CV of the two most important attributes, body length and maximum length, slightly increased in Phase 3. However the increase is not significant to generalize (p > 0.05), we explored individual assemblages including multiple stemmed points that could show a more clear pattern. The four assemblages in Suyanggae and Yongsandong sites show that CV values decreased with narrower confidence intervals, which means a high degree of precision (Figure 8<== not included yet). This could indicate the stronger connections within the groups during Phase 3.

>>>>

Compared to the Phase 2 and 3, we found that there are only minor differences between the two phases. The CV of the two most important attributes, body length and maximum length, slightly increased in Phase 3. However the increase is not significant to generalize (p \> 0.05), we explored individual assemblages including multiple stemmed points that could show a more clear pattern. The four assemblages in Suyanggae and Yongsandong sites show that CV values decreased with narrower confidence intervals, which means a high degree of precision (Figure 8\<== not included yet). This could indicate the stronger connections within the groups during Phase 3.
